---
title: "Case Study: Covid19 Analysis"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load data

```{r}
library(tidyverse)

raw_covid19_confirmed <- read_csv("https://bit.ly/covid19_confirmed")

raw_covid19_deaths <- read_csv("https://bit.ly/covid19_deaths")

raw_covid19_recovered <- read_csv("https://bit.ly/covid19_recover")
```

## Observe

```{r}
head(raw_covid19_confirmed)


```

## Your Turn - 01


1. Tidy all three data sets : 
- confirmed
- deaths
- recovered

```{r}
confirmed <- pivot_longer(data,
      cols = 5:ncol(data),
      names_to = "date",
      values_to = "count"
    ) 
    

 
 
 



```

2. Filter out the country by Nepal and remove unused variables.

- raw_confirmed_nepal
- raw_deaths_nepal
- raw_recovered_nepal


```{r}
# install.packages("janitor")

raw_confirmed_nepal <- confirmed %>% 
  janitor::clean_names() %>% 
  filter(country_region == "Nepal") %>% 
  select(-province_state, -long, -lat, -country_region)


```


3. Convert date variable into date format and add their respective 'type' variable.

- confirmed_nepal
- deaths_nepal
- recovered_nepal

```{r}
confirmed_nepal <- raw_confirmed_nepal %>% 
  mutate(date = mdy(date), 
         type = "confirmed"
         ) 
         

```

4. Bind them into a variable named **covid19_nepal**

```{r}
covid19_nepal



```


## Your Turn - 02

1. Make sure the data set is tidy

2. Try to visualize using **geom_line()**

```{r}

covid19_nepal 






```


## Cumulative vs Daily

- daily_count = current_cumulative_count - previous_cumulative_count

```{r}
covid19_nepal_daily <- covid19_nepal %>%
  group_by(type) %>%
  mutate(daily_count = count - lag(   , default = 0)) %>% 
  ungroup()

covid19_nepal_daily
```

## Your Turn - 03 

```{r}
covid19_nepal_daily %>% 
ggplot(aes(x = date, y = , color = type)) +
  geom_line()

```

```{r}
last_30_days <- covid19_nepal_daily %>%
  filter(
    date > Sys.Date() - 31,
    type == "confirmed"
  )

last_30_days
```

## Last 30 days plot

```{r}
30_days_plot <- last_30_days %>%
  ggplot(
    aes(x = date, y = daily_count)
  ) +
  geom_col()

30_days_plot
```

## Add Text Label

```{r}
plot_2 <- 30_days_plot +
  geom_text(
   aes(label = daily_count),
    hjust = -0, # horizontal justify
    angle = 45,   # change angle of text
    size = 0      # font-size
  ) # + 
#  scale_y_continuous(expand = c(.1, .1)) 



plot_2
```


## Add title 

```{r}
plot_3 <- plot_2 +
  labs(title = "", 
       caption = "")

plot_3
```

## Custom theme 

```{r}
mytheme <-  theme_classic() +
  theme(
    plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"),
    plot.title = element_text(
      hjust = 0.5, vjust = 5,
      size = 15,
      color = "black"
    )
  )


```

## Add theme

```{r}
plot_4 <- plot_3 +
  my_theme
  

plot_4
```
